---
title: "Corona Virus Report"
author:
- familyname: XXXX
  othernames: XXX
  address: Monash Universtidy
  email: XXX
  correspondingauthor: true
  qualifications:  XXX
- familyname: XXXX
  othernames: Reports
  address: XXX
  qualifications: XXX
- familyname: XXX
  othernames: XXX
  address: XXX
  email: XXX
  correspondingauthor: true
  qualifications:  XXX
department: Our consultancy \newline add names &\newline add names
organization: Australian Government COVID19
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---

```{r , echo = FALSE, message = FALSE, warning = FALSE}
# Libraries

library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)

```

```{r}
#Loading dataset

wwc <- read_csv("data/worldwidecases.csv")
```

\section*{Country XX1 and YY1"}
```{r table1}
wwc %>%
  filter(countriesAndTerritories == "India" | countriesAndTerritories == "China") %>%
  rename(country = countriesAndTerritories) %>%
  group_by(country) %>%
  summarise(deaths = sum(deaths),
            cases = sum(cases),
            ) %>%
  kable(col.names = c("Countries",
                           "Deaths",
                           "Cases"), caption = 'Total cases at the time of this report.') %>%
  kable_styling()

```

The Table \@ref(table:table1)) shows that China has far more deaths and total number of cases compared to India

```{r figure1}
wwc %>%
  filter(countriesAndTerritories == "India" | countriesAndTerritories == "China",
         year == 2020) %>%
  rename(country = countriesAndTerritories) %>%
  ggplot(aes(x = month, y = deaths, color = country)) +
  geom_smooth() +
  facet_wrap(~country) +
  theme_minimal() +
  ggtitle("Relationship between total cases and total deaths")
```
The Figure \@ref(fig:figure1)) show that while the Total number of cases in China are far superior, the death count is very much on a decline since February, while the death count in India has been increase quite rapidly since March.

\section*{Country: US and UK}

``` {r}
world <- read_csv("Data/worldwidecases.csv")


USUK <- world %>% filter (countryterritoryCode %in% c("USA", "GBR"))


```

``` {r fig1, fig.cap: "Deaths in the US and UK in April" }

plot1 <- USUK %>% filter(month == "4") %>% group_by(day, geoId, deaths) %>% summarise() %>%
ggplot(aes(x=day, y=deaths)) +
  geom_line()+
  facet_grid(~geoId)
plot1
```
Figure \@ref(fig:fig1) illustrates the number of death per day in the US and UK in April. The death tolls in US climb sharply to peak at nearly 5000 cases in mid April. In constrast, death cases number in UK stay relatively stable  

```{r tab1}
tab1 <- USUK %>% filter(month == "5") %>% group_by(day, geoId, deaths) %>% summarise() %>%
pivot_wider(names_from = geoId, values_from = deaths) %>%
kable(caption = "Number of deaths in US and UK in May")
```
 Table \@ref(tab:tab1) shows the number of deaths in US and UK in May.


Filter the dataset to present the countries of interest: 
  - France
  - Sweden
```{r filter-countries}
France <- wcc %>% 
  filter(countriesAndTerritories == "France") 
Sweden <- wwc %>%
  filter(countriesAndTerritories == "Sweden") 
  
```

Figure for countries
```{r glimpse-of-countries}
glimpse(france_and_sweden)
```

Table for France
```{r table-france}
table_france <- France %>%
  select(dateRep, cases, deaths) %>%
  arrange(desc(deaths)) %>%
  kable(caption = "Table showing the dates with higest number of confirmed cases and deaths for France") %>%
  kable_styling(bootstrap_options = c("hover", "striped"))
table_france
```



Table for sweden
```{r table-sweden-deaths-cases}
table_sweden <- Sweden %>% 
  select(dateRep, cases, deaths) %>%
  arrange(desc(deaths)) %>%
  kable(caption = "Table showing the dates with higest number of confirmed cases and deaths for Sweden") %>%
  kable_styling(bootstrap_options = c("hover", "striped"))
table_sweden
```

 


