---
title: "Corona Virus Report"
author:
- familyname: XXXX
  othernames: XXX
  address: Monash Universtidy
  email: XXX
  correspondingauthor: true
  qualifications:  XXX
- familyname: XXXX
  othernames: Reports
  address: XXX
  qualifications: XXX
- familyname: XXX
  othernames: XXX
  address: XXX
  email: XXX
  correspondingauthor: true
  qualifications:  XXX
department: Our consultancy \newline add names &\newline add names
organization: Australian Government COVID19
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---

```{r , echo = FALSE, message = FALSE, warning = FALSE}
# Libraries

library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)

```

```{r}
#Loading dataset

wwc <- read_csv("data/worldwidecases.csv")
```

\section*{Country XX1 and YY1"}
```{r table1}
wwc %>%
  filter(countriesAndTerritories == "India" | countriesAndTerritories == "China") %>%
  rename(country = countriesAndTerritories) %>%
  group_by(country) %>%
  summarise(deaths = sum(deaths),
            cases = sum(cases),
            ) %>%
  kable(col.names = c("Countries",
                           "Deaths",
                           "Cases"), caption = 'Total cases at the time of this report.') %>%
  kable_styling()

```

The Table \@ref(table:table1)) shows that China has far more deaths and total number of cases compared to India

```{r figure1}
wwc %>%
  filter(countriesAndTerritories == "India" | countriesAndTerritories == "China",
         year == 2020) %>%
  rename(country = countriesAndTerritories) %>%
  ggplot(aes(x = month, y = deaths, color = country)) +
  geom_smooth() +
  facet_wrap(~country) +
  theme_minimal() +
  ggtitle("Relationship between total cases and total deaths")
```
The Figure \@ref(fig:figure1)) show that while the Total number of cases in China are far superior, the death count is very much on a decline since February, while the death count in India has been increase quite rapidly since March.

\section*{Country XX2 and YY2}

\section*{Country XX3 and YY3}

Filter the dataset to present the countries of interest: 
  - France
  - Sweden
```{r filter-countries}
France <- wcc %>% 
  filter(countriesAndTerritories == "France") 
Sweden <- wwc %>%
  filter(countriesAndTerritories == "Sweden") 
  
```

Figure for countries
```{r glimpse-of-countries}
glimpse(france_and_sweden)
```

Table for France
```{r table-france}
table_france <- France %>%
  select(dateRep, cases, deaths) %>%
  arrange(desc(deaths)) %>%
  kable(caption = "Table showing the dates with higest number of confirmed cases and deaths for France") %>%
  kable_styling(bootstrap_options = c("hover", "striped"))
table_france
```



Table for sweden
```{r table-sweden-deaths-cases}
table_sweden <- Sweden %>% 
  select(dateRep, cases, deaths) %>%
  arrange(desc(deaths)) %>%
  kable(caption = "Table showing the dates with higest number of confirmed cases and deaths for Sweden") %>%
  kable_styling(bootstrap_options = c("hover", "striped"))
table_sweden
```

 


